Learning From Massive Noisy Labeled Data for Image Classification

### 2015-03-25 paper.tex
Add authors and describe the effect of M-Step in another way

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm2e}

@@

% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

%%%%%%%%% TITLE
\title{Learning From Massive Noisy Labeled Data for Visual Classification}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

@@

The semantic meaning of this optimization process is straight forward. We enumerate all the possible true labels, and weight each of them by their posterior probability based on our observation of the image and corresponding noisy label. Then we use these weighted labels to supervise the training of our deep neural networks.
% subsection learning_the_parameters (end)

@@

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm2e}
\usepackage{authblk}

@@

\cvprfinalcopy % *** Uncomment this line for the final submission

@@

%%%%%%%%% TITLE
\title{Learning From Massive Noisy Labeled Data for Image Classification}

\author[1]{Tong Xiao}
\author[2]{Tian Xia}
\author[2]{Yi Yang}
\author[2]{Chang Huang}
\author[1]{Xiaogang Wang}

\affil[1]{The Chinese University of Hong Kong}
\affil[2]{Baidu Research}

\renewcommand\Authands{ and }

% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both

@@

The M-Step above is equivalent to minimize the cross entropy between the estimated ground truth distribution and the prediction of the classifier.
% subsection learning_the_parameters (end)

@@

\section*{Acknowledgements}
\label{sec:acknowledgements}
This work is supported by the National Basic Research Program of China (973 program No. 2014CB340505).
